Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-11-02 paper-kelompok/main.tex
figure refrencing
author block formatting and sensor dfd

@@

\author{\IEEEauthorblockN{Alzana Armaniar Farhani}
\IEEEauthorblockA{\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
Email: farhanialzana@gmail.com}
\and
\IEEEauthorblockN{Balkan Khilmi Assakandari}
\IEEEauthorblockA{\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
Email: balkankhilmi@gmail.com}
\and
\IEEEauthorblockN{Anindhita Nayazirly}
\IEEEauthorblockA{\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
Email: zirlysukarno@gmail.com}
\and
\IEEEauthorblockN{Akhmadi Surawijaya}
\IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
Email:}
\and
\IEEEauthorblockN{Muhammad Ogin Hasanuddin}
\IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
Email:}
}

@@

\section{Methods}
\subsection{System Overview}
The proposed system consists of five subsystems which are light source, light sensor, control, user interface, and power subsystem. Its data flow diagram (DFD) can be seen in Fig. 1. The light sensor subsystem is composed of a slit, a monochromator, and an array of photodetector. The source light, which is emitted by a polychromatic light source, will be passed through the sample droplet located on an electrode of a DMF platform. The light which is not absorbed by the droplet will pass through the slit then to a monochromator. The monochromator decomposes the light into monochromatic light to be detected by the photodetector array. Each detector in the array measures the light intensity for a specific wavelength. The measurement readings will be sent to the control subsystem to be computed into absorbance values.

@@

\subsection{Light Sensor Subsystem}
The light sensor subsystem functions as a spectrometer that receives polychromatic light beam and outputs light intensities of discrete wavelengths in the form of digital data.
Polychromatic light beam enters the sensor subsystem through a hole and gets diffracted by a transmissive diffraction grating as to spatially separate light by its wavelengths.
The grating has a groove density of 1200 lines per millimeter, thus only the first order of diffraction is usable to separate the visible spectrum.
The resulting ray is then recorded by Micron® Imaging MT9M001 Monochrome CMOS digital image sensor.
Different pixel of the image sensor captures the intensity of different wavelengths ranging from 400 nanometer to 700 nanometer formatted into 10-bit unsigned integer.
The light sensor subsystem outputs, at maximum, 1280 16-bit unsigned integer values, each value representing the light intensity of certain wavelengths.

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.4]{light-sensor-dfd.png}}
    \caption{DFD of the light sensor subsystem.}
    \label{light-sensor-dfd}
    \end{figure}

@@

\subsection{User Interface Subsystem}
The user interface subsystem plays a role in connecting the system and the users. This can be done by interpreting the commands given by users through the input interface devices and process it into control signals that will be sent to the control subsystem. The subsystem also has a function to display measurement data which include sample concentration values, sample absorbance spectrum, regression curves, menus, and settings. Fig. 5 shows the data flow diagram of the user interface subsystem.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.4]{ui-dfd.png}}
    \caption{DFD of the user interface subsystem.}
    \label{ui-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{power-dfd.png}}
    \caption{DFD of the power subsystem.}
    \label{power-dfd}
    \end{figure}

>>>>

\makeatletter
\newcommand{\newlineauthors}{%
  \end{@IEEEauthorhalign}\hfill\mbox{}\par
  \mbox{}\hfill\begin{@IEEEauthorhalign}
}
\makeatother

@@

\author{\IEEEauthorblockN{Alzana Armaniar Farhani}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
farhanialzana@gmail.com}
\and
\IEEEauthorblockN{Balkan Khilmi Assakandari}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
balkankhilmi@gmail.com}
\and
\IEEEauthorblockN{Anindhita Nayazirly}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
zirlysukarno@gmail.com}
\newlineauthors
\IEEEauthorblockN{Akhmadi Surawijaya}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
email}
\and
\IEEEauthorblockN{Muhammad Ogin Hasanuddin}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{School of Electrical Engineering} \\
\textit{and Informatics} \\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia \\
email}
}

@@

\section{Methods}
\subsection{System Overview}
The proposed system consists of five subsystems which are light source, light sensor, control, user interface, and power subsystem. Its data flow diagram (DFD) is shown in Fig. \ref{system-dfd}. The light sensor subsystem is composed of a slit, a monochromator, and an array of photodetector. The source light, which is emitted by a polychromatic light source, will be passed through the sample droplet located on an electrode of a DMF platform. The light which is not absorbed by the droplet will pass through the slit then to a monochromator. The monochromator decomposes the light into monochromatic light to be detected by the photodetector array. Each detector in the array measures the light intensity for a specific wavelength. The measurement readings will be sent to the control subsystem to be computed into absorbance values.

@@

\subsection{Light Sensor Subsystem}
The light sensor subsystem functions as a spectrometer that receives polychromatic light beam and outputs light intensities of discrete wavelengths in the form of digital data.
Polychromatic light beam enters the sensor subsystem through a hole and gets diffracted by a transmissive diffraction grating as to spatially separate light by its wavelengths.
The grating has a groove density of 1200 lines/mm, and the first order of diffraction is used to separate the visible spectrum.
The resulting ray is then recorded by a CMOS image sensor (Arducam MT9M001 Monochrome Camera Module).
Different pixel of the image sensor captures the intensity of different wavelengths ranging from 400 nanometer to 700 nanometer formatted into 10-bit unsigned integer.
The light sensor subsystem outputs, at maximum, 400 16-bit unsigned integer values, each value representing the light intensity of wavelengths in the visible spectrum range.

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.33]{light-sensor-dfd.png}}
    \caption{DFD of the light sensor subsystem.}
    \label{light-sensor-dfd}
    \end{figure}

@@

\subsection{User Interface Subsystem}
The user interface subsystem plays a role in connecting the system and the users. This can be done by interpreting the commands given by users through the input interface devices and process it into control signals that will be sent to the control subsystem. The subsystem also has a function to display measurement data which include sample concentration values, sample absorbance spectrum, regression curves, menus, and settings. Fig. \ref{ui-dfd} shows the data flow diagram of the user interface subsystem.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.43]{ui-dfd.png}}
    \caption{DFD of the user interface subsystem.}
    \label{ui-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{power-dfd.png}}
    \caption{DFD of the power subsystem.}
    \label{power-dfd}
    \end{figure}
